\section*{Ex6 - 32}

\begin{enumerate}
    \item {Every cyclic group is Abelian. True, because every cyclic group is isomorphic to either $ \mathbb{Z} $ or $ \mathbb{Z}_n $ for some $ n \ge 2 \in \mathbb{N} $ and these groups are Abelian}.
    \item {Every Abelian group is cyclic. False, because $ \mathbb{Z}_2 \oplus \mathbb{Z}_2 $ is not cyclic.}
    \item {$ \mathbb{Q} $ under addition is a cyclic group. False, because if $ \mathbb{Q} $ were cyclic, then it has a generator $ \frac{p}{q} $, but then it cannot generate $ \frac{p}{2q} $.}
    \item {Every element of every cyclic group generate the group. False, the identity element always only generate itself, so unless the group is $ \{0\} $, it never generates the group.}
    \item {There is at least one Abelian group for every finite order $ > 0 $. True, $ \mathbb{Z}_n $ is such a group.}
    \item {Every group with order $ \le 4 $ is cyclic. False, $ \mathbb{Z}_2 \oplus \mathbb{Z}_2 $ is not cyclic.}
    \item {All generators of $ \mathbb{Z}_{20} $ is a prime number. False, 9 generates $ \mathbb{Z}_{20} $.}
    \item {If $ G $ and $ G' $ are groups, then $ G \cap G' $ is a group. False, it isn't even clear which operation to use.}
    \item {If $ H $ and $ K $ are subgroups of a group $ G $, then $ H \cap K $ is a group. True - for each pair of elements $ i, j \in H \cap K $, so $ j^{-1} \in H \cap K $, $ ij^{-1} \in H \cap K $.}
    \item {Every cyclic group of order $ > 2 $ has at two distinct generators. True, for any cyclic group with generator $ g $, $ g^{-1} $ is also a generator. Now if $ g = g^{-1} $, we will have $ g^2 = 1 $ and that contradicts with the fact that the group has order $ > 2 $. Therefore we have at least two distinct generators. }
\end{enumerate}