\subsubsection*{Exercise 0.3.2. (Cecilia, Gapry)}

\begin{flushleft}
Introduction \\
\vspace{10px}

We can use the \textbf{Well Ordering Property of} $\mathbb{N}$ to prove that 
the \textbf{Principle of Strong Induction} is equivalent to the 
\textbf{Standard Induction}. First, we prove that the \textbf{Well Ordering 
Property of} $\mathbb{N}$ is equivalent to the \textbf{Standard Induction}.  
Second, we prove that the \textbf{Well Ordering Property of} $\mathbb{N}$ is 
equivalent to the \textbf{Principle of Strong Induction}. So we can conclude 
that the \textbf{Principle of Strong Induction} is equivalent to the 
\textbf{Standard Induction}.
\end{flushleft}

\begin{flushleft}
Part A: \textbf{Well Ordering Property of} $\mathbb{N}$ is equivalent to the 
\textbf{Standard Induction}. \\
\vspace{10px}

Prove: \textbf{Well Ordering Property of} $\mathbb{N}$ $\implies$ 
\textbf{Standard Induction} is true. \\
\vspace{10px}

Proof by Contradiction: If the \textbf{Well Ordering Property of} $\mathbb{N}$ 
is true, and the \textbf{Standard Induction} is false. Then it follows that there 
exists a statement $P(n)$ which is false for some $n \in \mathbb{N}$, and if $P(1)$ 
is true and $P(k) \implies P(k + 1)$ is also true for all $k \in \mathbb{N}$. Let's 
define two sets, one is $S_F = \{ n \in \mathbb{N} |\ P(n) \text{ is false } 
\}$, the other is $S_T = \{ m \in \mathbb{N} |\ P(m) \text{ is true } \}$, 
$n \ne m$. According to \textbf{Well Ordering Property of} $\mathbb{N}$, we
know that $S_F$ has a least element $l$ such that $P(l)$ is false, it follows 
$ l - 1 \in S_T$ since $l - 1$ is less than the least index of $S_F$. $P(l - 1)$ 
is true. For now, we know $P(l - 1) \implies P(l)$ is false which  
contradicts with our assumption $P(k) \implies P(k + 1)$ is true for all $k \in 
\mathbb{N}$. Hence, we  know that \textbf{Well Ordering Property of} $\mathbb{N}$ 
$\implies$ \textbf{Standard Induction} is true.
\end{flushleft}

\begin{flushleft}
Prove: \textbf{Standard Induction} $\implies$ \textbf{Well Ordering Property 
of} $\mathbb{N}$ is true. \\
\vspace{10px}

The contraposition of \textbf{Well Ordering Property of} $\mathbb{N}$ is
that if the least element doesn't exist, then $S$ is the empty set. 
Let's use standard induction to prove the following statement is true. \\
\vspace{10px}

$ P(k) $: If $ S $ does not have a least element, then $\{1, \cdots, k\} \cap S$ 
is the empty set.
\vspace{10px}

(i) Basis Step: If $ 1 \in S $, then $ 1 $ is the least element. But $ S $ does not 
have a least element. Therefore $ 1 \notin S $ and so $\{1, \cdots, 1\} \cap S$ is 
the empty set.
\vspace{10px}

(ii) Induction Step: 
Assume P(k) is true, then $\{1, \cdots, k\} \cap S$ is the empty set. For now, 
If $k + 1 \in S$, then it is the least element of $S$. But $ S $ does not 
have a least element. Therefore $ k + 1 \notin S $ and $\{1, \cdots, k, k + 1\}
 \cap S$ is the empty set.\\
\vspace{10px}

Since none of the natural number can be in $ S $, it follows that $ S $ is the empty set.
\vspace{10px}
 
Since the contraposition of \textbf{Well Ordering Property of} $\mathbb{N}$ is 
true, the \textbf{Well Ordering Property of} $\mathbb{N}$ is also true. So, we 
know that \textbf{Standard Induction} $\implies$ \textbf{Well Ordering Property 
of} $\mathbb{N}$ is true. 
\end{flushleft}

\begin{flushleft}
Hence, we can conclude that \textbf{Well Ordering Property of} $\mathbb{N}$ is 
equivalent to the \textbf{Standard Induction}. \\
\end{flushleft}

\begin{flushleft}
Part B: \textbf{Well Ordering Property of} $\mathbb{N}$ is equivalent to the 
\textbf{Principle of Strong Induction}. \\
\vspace{10px}

Prove: \textbf{Well Ordering Property of} $\mathbb{N}$ $\implies$ 
\textbf{Principle of Strong Induction} is true. \\
\vspace{10px}

Proof by Contradiction: If the \textbf{Well Ordering Property of} $\mathbb{N}$ 
is true, and the \textbf{Strong Induction} is false. Then it follows that there 
exists a statement $P(n)$ is false for some $n \in \mathbb{N}$, $P(1)$ is true 
and $P(1) \land \cdots \land P(k) \implies P(k + 1)$ is also true for all $k \in 
\mathbb{N}$. Let's define two sets, one is $S_F = \{n \in \mathbb{N} |\ 
P(n) \text{ is false } \}$, the other is $S_T = \{m \in \mathbb{N}  |\ P(m)
 \text{ is true } \}$, $n \ne m$. According to \textbf{Well Ordering Property of} 
$\mathbb{N}$, we know $S_F$ has a least element $l$ such that $P(l)$ is false, 
it follows that $ 1, \cdots, l - 1$ are all in $S_T$ since $1, \cdots, 
l - 1$ are all less than $l$. For now, we know that $P(1) \land \cdots \land 
P(l - 1)$ is true,  $P(l)$ is false. It follows that $P(1) \land \cdots \land 
P(l - 1) \implies P(l)$ is false which contradicts with our assumption $P(1) 
\land \cdots \land P(k) \implies P(k + 1)$ is true for all $k \in 
\mathbb{N}$. Hence, we know \textbf{Well Ordering Property of} $\mathbb{N}$ 
$\implies$ \textbf{Principle of Strong Induction} is true.
\end{flushleft}

\begin{flushleft}
Prove: \textbf{Principle of Strong Induction} $\implies$ \textbf{Well Ordering 
Property of} $\mathbb{N}$ is true. \\
\vspace{10px}

The contraposition of \textbf{Well Ordering Property of} $\mathbb{N}$ is that 
if the least element doesn't exist, then $S$ is the empty set. Let's use strong 
induction to prove the following statement is true. \\
\vspace{10px}

$ P(k) $: If $ S $ does not have a least element, then $ k \notin S$ 
\vspace{10px}

(i) Basis Step: If $ 1 \in S $, then $ 1 $ is the least element. But $ S $ does not 
have a least element. Therefore $ 1 \notin S $.
\vspace{10px}

(ii) Induction Step: 
If $P(1), \cdots, P(k)$ are all true, then $1, \cdots, k$ are all not in $S$, 
For now, If $k + 1 \in S$, then it is the least element of $S$. It follows that 
$k + 1 \notin S$ \\
\vspace{10px}

Since none of the natural number can be in $ S $, it follows that $ S $ is the empty set.
\vspace{10px}

Since the contraposition of \textbf{Well Ordering Property of} $\mathbb{N}$ is 
true, the \textbf{Well Ordering Property of} $\mathbb{N}$ is also true. Hence, 
\textbf{Principle of Strong Induction} $\implies$ \textbf{Well Ordering 
Property of} $\mathbb{N}$ is true.
\end{flushleft}

\begin{flushleft}
Hence, we can conclude that \textbf{Well Ordering Property of} $\mathbb{N}$ is 
equivalent to the \textbf{Principle of Strong Induction}. \\
\end{flushleft}

\begin{flushleft}
Summary \\
\vspace{10px}

According to the results of Part A and Part B, we know that the 
\textbf{Principle of Strong Induction} is equivalent to the \textbf{Standard 
Induction} is true. Q.E.D.
\end{flushleft}
