\section*{Problem 16}
\subsection*{Part a}
Denote $ h $ to be the height of the trapezoid $ BCDE $, it is also the height of $ \triangle BCF $, therefore $ h = \frac{\sqrt{3}x}{2} $.

Now the area of the trapezoid can be represented two ways.

\begin{eqnarray*}
                      \frac{1}{2}(BE + CD)h &=& 5\sqrt{3} \\
  \frac{1}{2}(6 + (6-x))\frac{\sqrt{3}x}{2} &=& 5\sqrt{3} \\
                               (6 + (6-x))x &=& 20        \\
                             x^2 - 12x + 20 &=& 0
\end{eqnarray*}

With the equation, it is easy to solve for $ x $ as follows:
\begin{eqnarray*}
    x^2 - 12x + 20 &=& 0 \\
    (x - 10)(x - 2) &=& 0 \\
                 x &=& 10 \text{ or } 2
\end{eqnarray*}
But it is obvious that $ x $ cannot be 10 because $ CD = 6 - x = -4 $, which is impossible. Therefore $ x = 2 $.

\subsection*{Part b}
\subsubsection*{Part i}
$ |A'E| = |AE| = 6 $, $ |DE| = x = 2 $, therefore we can find $ |A'D| $ using the cosine rule.

\begin{eqnarray*}
  |A'D|^2 &=& |A'E|^2 + |DE|^2 - 2|A'E||DE| \cos \angle A'ED \\
  |A'D|^2 &=& 6^2 + 2^2 - 2 \times 6 \times 2 \cos 40^\circ \\
    |A'D|^2 &=& 40 - 24 \cos 40^\circ \\
        |A'D| &=& \sqrt{40 - 24 \cos 40^\circ} \\
        |A'D| & \approx & 4.65 \text{cm}
\end{eqnarray*}

\subsubsection*{Part ii}
To solve this part, adding the point $ F $ on the line $ EA $ such that $ |EF| = 2 $ before the folding, the line $ DF $ would intersect $ EB $ at a new point we name $ O $. After folding, the point will turn into $ F' $, and so the angle between the two planes in $ \angle F'OD $.

To compute $ \angle F'OD $, we will leverage this new coordinate system. Let $ O $ be the origin. $ OB $ will be the x-axis, $ OD $ will be the y-axis and the z-axis will be the implied one by the right handed coordinate system so that $ A' $ will be positive $ z $ coordinate. Now we list the coordinates of the interesting points.

\begin{enumerate}
    \item{Point $ O $ has coordinate $ (0, 0, 0) $. }
    \item{Point $ E $ has coordinate $ (-1, 0, 0) $. }
    \item{Point $ D $ has coordinate $ (0, \sqrt{3}, 0) $. }
    \item{Point $ F' $ has coordinate $ (0, y, z) $, where $ y $ and $ z $ are currently unknown. }
\end{enumerate}

The vectors $ \vec{ED} = -\vec{i} + \sqrt{3}\vec{j} $ and $ \vec{EF'} = -\vec{i} + y\vec{j} + z\vec{k} $, therefore the dot product is $ \vec{ED} \cdot \vec{EF'} = 1 + y\sqrt{3} $.

But we also know the dot product is $ |ED||EF'| \cos(40^\circ) $, so we can solve for $ y $
\begin{eqnarray*}
    1 + y\sqrt{3} &=& |ED||EF'| \cos 40^\circ             \\
    1 + y\sqrt{3} &=& 2 \times 2 \times \cos 40^\circ     \\
               y &=& \frac{4 \cos 40^\circ - 1}{\sqrt{3}}
\end{eqnarray*}

Now we can compute $ \angle F'OD $ using the dot product formula again.

On one hand, we can compute the dot product using cosine formula:
\begin{eqnarray*}
     |OD| &=& \sqrt{3} \\
    |OF'| &=& \sqrt{3} \\
    \vec{OD} \cdot \vec{OF'} &=& |OD||OF'| \cos \angle F'OD \\
    &=& 3 \cos \angle F'OD \\
\end{eqnarray*}

On the other hand, we compute that using the vectors:
\begin{eqnarray*}
    \vec{OD} &=& \sqrt{3}\vec{j} \\
    \vec{OF} &=& y\vec{j} + z\vec{k} \\
    \vec{OD} \cdot \vec{OF'} &=& y\sqrt{3} \\
\end{eqnarray*}

So we have $ \angle F'OD = \arccos \frac{y\sqrt{3}}{3} = \arccos \frac{4 \cos 40^\circ - 1}{3} \approx 46.5^\circ $.

\subsubsection*{Part iii}
To find the coordinate of $ A' $, we can extend $ EF' $, therefore we want to find $ z $.

The length of $ OF' $ is $ \sqrt{3} $, but it is also $ \sqrt{y^2 + z^2} $, therefore $ y^2 + z^2 = 3 $, and so we can solve for $ z = \sqrt{3 - y^2} \approx 1.257 $.

Now the coodinate of $ A' $ is obvious, it is $ (2,3y,3z) = (-1,0,0) + 3(1,y,z) $. The $ z $ coordinate of $ A' $ is the altitude of the pyramid, therefore the volume of the pyramid is $ \frac{1}{3}(3z)(5\sqrt{3}) = 5z\sqrt{3} \approx 10.885 $.
